Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-03-14 PAPER.tex
went through Adrian's edits and made his proposed suggestions

The quantity $P_{\rm in}$, defined by Equation \eqref{eq:Pin}, is a uniformly weighted estimator of the power spectrum of $\mathbf{e}$. Since there is no noise contribution to $\mathbf{e}$, it can be considered the power spectrum of this particular realization of the EoR; alternatively, it can be viewed as the true power spectrum of the injected signal up to cosmic variance fluctuations. The role of $P_{\rm in}$ in our analysis is to serve as a reference for the power spectrum that would be measured if there were no signal loss or other systematics. This is then to be compared to $P_{\rm out}$, which approximates the (lossy) power spectrum estimate that is outputted by our analysis pipeline prior to any signal loss adjustments. In principle, one could compute $P_{\rm out}$ using end-to-end simulations of the instrument and data analysis pipeline. In practice, however, such simulations may not accurately reflect real-life systematics and foregrounds. To overcome this obstacle, one can make the assumption that since the EoR signal is expected to be small, the data vector $\mathbf{x}$ itself is our best model of these contaminants. Making this assumption, the injected EoR signal $\mathbf{e}$ takes on the role of the true EoR signal, and the sum of $\mathbf{x}$ and $\mathbf{e}$ (i.e., Equation \eqref{eq:rxe}) replaces $\mathbf{x}$ as our model of the measured data.
\cc{explain why we evaluate $P_{out}$ at $p_{r}$} \acl{Added! See how you like it}
%In the limit where no significant cross correlations between the data and the injected signals are found, this will recover the amount of injected power spectrum remaining after the covariance weighting operation (i.e. the amount of background EoR power, $P_{\rm eor}$, not removed by the foreground down-weighting procedure). In other words, we make the anzatz that

@@

\begin{eqnarray}
\label{eq:crossterm}
P_{\rm out,\alpha} &= &  \text{M}^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} + \text{M}^{\alpha}_{b}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}
^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
&+& 2 \text{M}^{\alpha}_{c}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} %\nonumber \\
%&-& \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x}.
\end{eqnarray}
In order to investigate the effect of each of these terms on signal loss, all three components are plotted in Figure \ref{fig:sigloss_terms} for two cases: \acl{can we go through and add the word ``empirical"? The phrase ``inverse covariance weight" should be reserved for when one is weighting by the true inverse covariance.} inverse covariance weighting ($\textbf{R}_{r} = \widehat{\textbf{C}}_{r}^{-1}$) and uniform-weighted ($\textbf{R}_{r} = \textbf{I}$). We will now examine the behavior of this equation in the regimes of very weak and very strong injected signal.

{\bf Small injection:}
In this regime, the first term in Equation \eqref{eq:crossterm} is very similar to the power spectrum of data alone, namely $\text{M}^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} \sim \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x}$. They differ only in their covariance matrices, and when the injected signal is very small compared to the data, their difference can be neglected. This is shown by the black and gray curves converging in both panels of Figure \ref{fig:sigloss_terms}. In this regime, we also note that the cross-terms (red) behave as noise, even in the inverse covariance weighted case (left plot), spanning a range of values set by the injection level. This is because $\widehat{\textbf{C}}_{r}$ is dominated by the data $\textbf{x}$, avoiding correlations with $\textbf{e}$ that can lead to solely negative power (explained further below)%In this limit we might imagine that the cross-correlation should also be small, enabling us to recover just the EoR term. However, examining the cross-term plotted in Figure \ref{fig:sigloss_terms} (red) in the identity case (right plot), we see that this term is still large enough to have a significant impact on $P_{\rm out}$. It is in this regime where we're dominated by biases from the cross-terms, causing the difference between the signal-only term (green) and $P_{\rm out}$ (black). We also note that the cross-terms behave as noise at small injections even in the inverse covariance weighted case (left plot), spanning a range of values set by the injection level. This is because $\widehat{\textbf{C}}_{r}$ is dominated by the data $\textbf{x}$, avoiding correlations with $\textbf{e}$ that can lead to solely negative power (explained further below).

{\bf Large injection:}
When the injected signal (red) is much larger than the data-only power spectrum (gray), the data-only components can 
be neglected as many orders of magnitude smaller. As we can see from Figure \ref{fig:sigloss_terms}, the cross-terms (red) are also small in comparison to the signal-only term (green). Here only does the signal-only term recover the ``loss'' injected simulated EoR signal as intended (i.e. the black and green curves agree). We again see that the cross-terms behave as noise at large injections in the inverse covariance weighted case for a similar reasoning as it does at small injections --- here $\widehat{\textbf{C}}_{r}$ is dominated by the signal $\textbf{e}$, avoiding correlations with $\textbf{x}$.

@@

\begin{figure*}
	\centering
	\includegraphics[width=1\textwidth]{plots/sigloss_terms.png}
	\caption{Illustration of the power spectrum components used to estimate signal loss, as defined by Equation \eqref{eq:crossterm} for PAPER-64 data for the inverse covariance weighted case (left) and uniform-weighted case (right). The details of the simulation used to generate the figure is explained in Section \ref{sec:Practice}; here we fit smooth polynomials to our data points to create the curves. We show the contributions of three signal loss terms (blue, red, green), which when combined via Equation \eqref{eq:crossterm} produce the black curve ($\widehat{\textbf{p}}_{r}$). The gray curve is the power spectrum value of data alone. Most notably, the green curves (the signal-only term) denotes the signal loss analysis used in \citetalias{ali_et_al2015}, and the red curves showcase the importance of the cross-terms in computing signal loss. As explained in the main text, the cross-terms behave as noise (with some range of values), for very small and large injection levels. For the inverse covariance weighted case, it is in these extreme regimes when $\widehat{\textbf{C}}_{r}$ is dominated by either $\textbf{x}$ (low injects) or $\textbf{e}$ (large injects). However, at power levels comparable to the data (the middle region), the cross-terms can produce large, negative signal due to the couplings between $\textbf{x}$ and $\textbf{e}$ which affect $\widehat{\textbf{C}}_{r}$. This causes the difference between the green curve (which exhibits negligible loss at the data level) and the black curve (which exhibits $\sim$$3$ orders of magnitude of loss at the data level for the inverse covariance weighted case). Finally, the dotted diagonal black line represents perfect unity transfer, or no signal loss, which we recover for the uniform-weighted case.}
	\label{fig:sigloss_terms}
\end{figure*}

@@

The correlation between $\widehat{\textbf{C}}_r^{-1}\textbf{e}$ and $\widehat{\textbf{C}}_r^{-1}\textbf{x}$ means that we cannot compute signal loss using a signal-only 
simulation, which would yield greater values for $P_{\rm out}$ and thereby underestimate signal loss. This argument is also made in \citet{switzer_et_al2015} in regards to estimating loss associated with the foreground cleaning of Green Bank Telescope (GBT) data. \acl{The following line is no longer true}Therefore, in our revised 
signal loss computation we use the full quantity for $P_{\rm out}$ as defined in Equation \eqref{eq:sigloss}, which subtracts the 
weighted power spectrum of the data from the weighted power spectrum of data plus EoR.

@@

We now shift our attention towards computing upper limits on the EoR signal for the fringe-rate filtered PAPER-64 dataset in a way that accounts for signal loss. While our methodology 
outlined below is independent of weighting scheme, here we demonstrate the computation using inverse covariance weighting 
($\textbf{R} = \widehat{\textbf{C}}^{-1}$), the weighting scheme used in \citetalias{ali_et_al2015} which, with an empirically estimated covariance, leads to substantial loss. With this weighting, our 
expressions for $P_{\rm in}$ and $P_{\rm out}$ become:

@@

\cc{need edits in this section} \acl{Done!} Phrased in the context of Bayes' rule, we wish to find the posterior probability distribution $p(P_{\rm in} | 
P_{\rm out})$, which is the probability of $P_{\rm in}$ given the uncorrected/measured power spectrum estimate $P_{\rm out}$. Bayes' rule gives

@@

Going forward, we treat every $k$-value separately in order to determine an upper limit on EoR per $k$. For every injection level, we smooth the distribution of $P_{\rm out}$ values using kernel density estimators (\citealt{scott2008kernel}), normalizing each one. Stitching all of them together results in a 2-dimensional smoothed transfer function, shown in Figure \ref{fig:sigloss_transfercurve} for inverse covariance weighting (left) and uniform weighting (right). \acl{Why not use $P_{\rm out}$ on the vertical axes of these plots?} Although we only show figures for one $k$-value, we note that 
the shape of the transfer curve is nearly identical for all $k$'s. This transfer function is the likelihood function in Bayes' rule, namely $\mathcal{L} (  P_{\rm out} | P_{\rm in})$. After multiplying by the prior \acl{right?}, we then simply take a horizontal cut across at the data value $P_{\rm out}$ to yield a posterior distribution for the signal. We compute the $95\%$ confidence interval (an upper limit on EoR) from these distributions.

@@

By-eye inspection of the transfer function plot in Figure \ref{fig:sigloss_transfercurve} gives a sense of what the signal loss result should be. The power spectrum value of our data, $
\widehat{\textbf{p}}_{x}$ is marked by the solid gray horizontal lines. From the left plot (inverse covariance weighting), one can eyeball that a data value of $10^{4} \, mK^{2} (h^{-1} Mpc)^{3}$, for example, would map approximately to a 
value of $\sim10^{8} \, mK^{2} (h^{-1} Mpc)^{3}$, implying a signal loss factor of $\sim10000$. For the uniform-weighted case (right plot), we see no loss at a data value of $\sim10^{7} \, mK^{2} (h^{-1} Mpc)^{3}$.

@@

\begin{figure*}
	\centering
	\includegraphics[width=1\textwidth]{plots/sigloss_transfercurve_posneg.png}
	\caption{Signal loss transfer functions showing the relationship of $P_{\rm in}$ and $\widehat{\textbf{p}}_{r}$, as defined by Equations \eqref{eq:Pin} and \eqref{eq:sigloss}. Power spectra values (black points) are generated for $20$ realizations of $\textbf{e}$ per signal injection level. Kernel density estimations of the power spectrum transfer functions are shown as colored 
heat-maps on top of the points for the cases of inverse covariance weighted PAPER-64 data (left) and uniform-weighted data (right). The dotted black 
diagonal lines mark a perfect unity mapping, and the solid gray horizontal line denotes the power spectrum value of the data $\widehat{\textbf{p}}_{x}$, from which a posterior distribution for the signal is extracted. From these plots, it is clear that inverse covariance weighting results in over $\sim3$ orders of magnitude of signal loss at the data level, whereas the uniform-weighted case does 
not exhibit loss. The general shape of these transfer functions are also shown by the black curves in Figure \ref{fig:sigloss_terms} for comparison.}
	\label{fig:sigloss_transfercurve}
\end{figure*}

@@

The loss-corrected power spectrum result for inverse covariance weighted PAPER-64 data is shown in Figure \ref{fig:ps2_data} (black dashed), which we can compare to the original lossy result (black and gray points). %There are a few important checks to examine. First, we see that the uniform-weighted power spectrum $2\sigma$ upper limit (dashed blue) is identical in both panels. This is an important check, as we expect no signal loss for this case. Any difference here would indicate an error in the pipeline or discrepancy in the range of data included. Additionally, it is clear that the power spectrum, prior to signal loss estimation, is inconsistent with the (now revised) theoretical noise level prediction. 
Post-signal loss estimation, the power spectrum limits are higher than both the theory (green) and uniform-weighted power spectrum (blue dashed), a consequence of weighting with a steep eigenspectrum where the `weak' modes are strongly coupled to the time-averaged fringe-rate filtered data. We elaborate on this point in the next section, as well as investigate alternate 
weighting schemes to inverse covariance weighting, with the goal of finding one that balances the aggressiveness of down-weighting contaminants and minimizing the loss of EoR signal.

\begin{figure*}
	\centering
	\includegraphics[width=0.4\textwidth]{plots/ps1_data.png}
	\includegraphics[width=0.4\textwidth]{plots/ps2_data.png}
	\caption{Full inverse covariance weighted power spectrum of PAPER-64 data pre-signal loss estimation (positive points in black and negative points in gray, 
with $2\sigma$ error bars). The dashed black curve is the $2\sigma$ upper limit on the EoR signal post-signal loss estimation. The dashed blue line is the uniform-weighted power 
spectrum ($2\sigma$ upper limit). The solid green line is the theoretical $2\sigma$ noise level prediction based on observational 
parameters, whose calculation is detailed in Section \ref{sec:PSSense}.}
	\label{fig:ps2_data}
\end{figure*}

@@

We also saw in Section \ref{sec:otherweight} how adding the identity matrix to the empirical covariance can minimize signal loss. We experiment with this idea as well, shown in the bottom panel of Figure \ref{fig:sigloss_modeloop}. The grey and black lines represent power spectrum limits pre and post signal loss estimation, respectively, as a function of the strength of $\textbf{I}$ that is added to $\widehat{\textbf{C}}$, quantified as the percentage of the $Tr(\widehat{\textbf{C}})$ added to $\widehat{\textbf{C}}$. When $0\%$  of the $Tr(\widehat{\textbf{C}})$ is used, it is equivalent to full inverse covariance weighting. From this plot we see that only a small percentage of $Tr(\widehat{\textbf{C}})$ is needed to significantly reduce loss. We expect that as the strength of $\textbf{I}$ is increased (going to the left), both the black and gray curves will approach the uniform-weighted case.

\begin{figure*}
	\centering
	\includegraphics[width=1\textwidth]{plots/sigloss_modeloop_2panel.png}
	\caption{Power spectra $2\sigma$ upper limits for $k=0.393$ h Mpc$^{-1}$ for fringe-rate filtered PAPER-64 data. Top: Values 
are shown before (gray) and after (black) signal loss estimation as a function of number of eigenmodes of $\widehat{\textbf{C}}$ that 
are down-weighted. This regularization knob is tuned from $0$ modes on the left (i.e. unweighted) to $21$ modes on the right (i.e. full inverse 
covariance weighting). Over $\sim3$ orders of magnitude of signal loss results when using inverse covariance weighting. Bottom: Power spectrum upper limits before (gray) and after (black) signal loss estimation as a function of identity added to the empirical covariance. This regularization knob is tuned from $0\%$  of the $Tr(\widehat{\textbf{C}})$ added to $\widehat{\textbf{C}}$ on the right (i.e. full inverse covariance weighting) to $20\%$ of $Tr(\widehat{\textbf{C}})$ added to $\widehat{\textbf{C}}$ on the left. Also 
plotted in both panels for comparison are $2\sigma$ power spectrum upper limits for the uniform-weighted case (dashed blue) and inverse variance 
weighted case (red); both are after signal loss estimation. Finally, a theoretical prediction for noise ($2\sigma$ error) is plotted 
as solid green. In the revised PAPER-64 analysis in this paper, we choose to use a regularization scheme of $\widehat{\textbf{C}} \equiv 0.04Tr(\widehat{\textbf{C}}) + \widehat{\textbf{C}}$ because it slightly outperforms both the down-weighting individual eigenmodes and inverse variance cases.}
	\label{fig:sigloss_modeloop}
\end{figure*}

@@

\begin{figure}[tp]
\centering
\includegraphics[width=\textwidth]{plots/method2_heatmap_posneg.png}
\caption{The distribution of $\widehat{\textbf{p}}_{r}$ values for a 
given injection level P$_{\rm in}$. The $\widehat{\textbf{p}}_{r}$ values that are plotted on the y-axis represent the weighted power spectrum of data plus the injected signal. It differs from that of Figure \ref{fig:sigloss_transfercurve} by not subtracting off the power spectrum of data alone (not subtracting off the second term in Equation \eqref{eq:sigloss}). We show kernel density estimations of the power spectrum transfer functions as colored heat-maps for the cases of inverse covariance weighted PAPER-64 data (left) and uniform-weighted data (right). The dotted black 
diagonal lines mark a perfect unity mapping, and the solid gray horizontal line denotes the peak of $\widehat{\textbf{p}}_{x}$, the data distribution. At low injection, $\widehat{\textbf{p}}_{r}$ converges to the data level.
}
\label{fig:Pr_vs_Pin}
\end{figure}

>>>>

The quantity $P_{\rm in}$, defined by Equation \eqref{eq:Pin}, is a uniformly weighted estimator of the power spectrum of $\mathbf{e}$. Since there is no noise contribution to $\mathbf{e}$, it can be considered the power spectrum of this particular realization of the EoR; alternatively, it can be viewed as the true power spectrum of the injected signal up to cosmic variance fluctuations. The role of $P_{\rm in}$ in our analysis is to serve as a reference for the power spectrum that would be measured if there were no signal loss or other systematics. This is then to be compared to $P_{\rm out}$, which approximates the (lossy) power spectrum estimate that is outputted by our analysis pipeline prior to any signal loss adjustments. In principle, one could compute $P_{\rm out}$ using end-to-end simulations of the instrument and data analysis pipeline. In practice, however, such simulations may not accurately reflect real-life systematics and foregrounds. To overcome this obstacle, one can make the assumption that since the EoR signal is expected to be small, the data vector $\mathbf{x}$ itself is our best model of these contaminants. Making this assumption, the injected EoR signal $\mathbf{e}$ takes on the role of the true EoR signal, and the sum of $\mathbf{x}$ and $\mathbf{e}$ (i.e., Equation \eqref{eq:rxe}) replaces $\mathbf{x}$ as our model of the measured data.

%In the limit where no significant cross correlations between the data and the injected signals are found, this will recover the amount of injected power spectrum remaining after the covariance weighting operation (i.e. the amount of background EoR power, $P_{\rm eor}$, not removed by the foreground down-weighting procedure). In other words, we make the anzatz that

@@

\begin{eqnarray}
\label{eq:crossterm}
P_{\rm out,\alpha} &= &  \text{M}^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} + \text{M}^{\alpha}_{b}\textbf{e}^{\dagger}\textbf{R}_{r}\textbf{Q}
^{\alpha}\textbf{R}_{r}\textbf{e} \nonumber \\
&+& 2 \text{M}^{\alpha}_{c}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{e} %\nonumber \\
%&-& \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x}.
\end{eqnarray}
In order to investigate the effect of each of these terms on signal loss, all three components are plotted in Figure \ref{fig:sigloss_terms} for two cases: empirical inverse covariance weighting ($\textbf{R}_{r} = \widehat{\textbf{C}}_{r}^{-1}$) and uniform-weighted ($\textbf{R}_{r} = \textbf{I}$). We will now examine the behavior of this equation in the regimes of very weak and very strong injected signal.

{\bf Small injection:}
In this regime, the first term in Equation \eqref{eq:crossterm} is very similar to the power spectrum of data alone, namely $\text{M}^{\alpha}_{a}\textbf{x}^{\dagger}\textbf{R}_{r}\textbf{Q}^{\alpha}\textbf{R}_{r}\textbf{x} \sim \text{M}^{\alpha}_{x}\textbf{x}^{\dagger}\textbf{R}_{x}\textbf{Q}^{\alpha}\textbf{R}_{x}\textbf{x}$. They differ only in their covariance matrices, and when the injected signal is very small compared to the data, their difference can be neglected. This is shown by the black and gray curves converging in both panels of Figure \ref{fig:sigloss_terms}. In this regime, we also note that the cross-terms (red) behave as noise, even in the empirically inverse covariance weighted case (left plot), spanning a range of values set by the injection level. This is because $\widehat{\textbf{C}}_{r}$ is dominated by the data $\textbf{x}$, avoiding correlations with $\textbf{e}$ that can lead to solely negative power (explained further below)%In this limit we might imagine that the cross-correlation should also be small, enabling us to recover just the EoR term. However, examining the cross-term plotted in Figure \ref{fig:sigloss_terms} (red) in the identity case (right plot), we see that this term is still large enough to have a significant impact on $P_{\rm out}$. It is in this regime where we're dominated by biases from the cross-terms, causing the difference between the signal-only term (green) and $P_{\rm out}$ (black). We also note that the cross-terms behave as noise at small injections even in the inverse covariance weighted case (left plot), spanning a range of values set by the injection level. This is because $\widehat{\textbf{C}}_{r}$ is dominated by the data $\textbf{x}$, avoiding correlations with $\textbf{e}$ that can lead to solely negative power (explained further below).

{\bf Large injection:}
When the injected signal (red) is much larger than the data-only power spectrum (gray), the data-only components can 
be neglected as many orders of magnitude smaller. As we can see from Figure \ref{fig:sigloss_terms}, the cross-terms (red) are also small in comparison to the signal-only term (green). Here only does the signal-only term recover the ``loss'' injected simulated EoR signal as intended (i.e. the black and green curves agree). We again see that the cross-terms behave as noise at large injections in the empirical inverse covariance weighted case for a similar reasoning as it does at small injections --- here $\widehat{\textbf{C}}_{r}$ is dominated by the signal $\textbf{e}$, avoiding correlations with $\textbf{x}$.

@@

\begin{figure*}
	\centering
	\includegraphics[width=1\textwidth]{plots/sigloss_terms.png}
	\caption{Illustration of the power spectrum components used to estimate signal loss, as defined by Equation \eqref{eq:crossterm} for PAPER-64 data for the empirical inverse covariance weighted case (left) and uniform-weighted case (right). The details of the simulation used to generate the figure is explained in Section \ref{sec:Practice}; here we fit smooth polynomials to our data points to create the curves. We show the contributions of three signal loss terms (blue, red, green), which when combined via Equation \eqref{eq:crossterm} produce the black curve ($\widehat{\textbf{p}}_{r}$). The gray curve is the power spectrum value of data alone. Most notably, the green curves (the signal-only term) denotes the signal loss analysis used in \citetalias{ali_et_al2015}, and the red curves showcase the importance of the cross-terms in computing signal loss. As explained in the main text, the cross-terms behave as noise (with some range of values), for very small and large injection levels. For the empirical inverse covariance weighted case, it is in these extreme regimes when $\widehat{\textbf{C}}_{r}$ is dominated by either $\textbf{x}$ (low injects) or $\textbf{e}$ (large injects). However, at power levels comparable to the data (the middle region), the cross-terms can produce large, negative signal due to the couplings between $\textbf{x}$ and $\textbf{e}$ which affect $\widehat{\textbf{C}}_{r}$. This causes the difference between the green curve (which exhibits negligible loss at the data level) and the black curve (which exhibits $\sim$$3$ orders of magnitude of loss at the data level for the empirical inverse covariance weighted case). Finally, the dotted diagonal black line represents perfect unity transfer, or no signal loss, which we recover for the uniform-weighted case.}
	\label{fig:sigloss_terms}
\end{figure*}

@@

The correlation between $\widehat{\textbf{C}}_r^{-1}\textbf{e}$ and $\widehat{\textbf{C}}_r^{-1}\textbf{x}$ means that we cannot compute signal loss using a signal-only 
simulation, which would yield greater values for $P_{\rm out}$ and thereby underestimate signal loss. This argument is also made in \citet{switzer_et_al2015} in regards to estimating loss associated with the foreground cleaning of Green Bank Telescope (GBT) data. Therefore, in our revised 
signal loss computation we use the full quantity for $P_{\rm out}$ as defined in Equation \eqref{eq:crossterm_full}.
weighted power spectrum of the data from the weighted power spectrum of data plus EoR.

@@

We now shift our attention towards computing upper limits on the EoR signal for the fringe-rate filtered PAPER-64 dataset in a way that accounts for signal loss. While our methodology 
outlined below is independent of weighting scheme, here we demonstrate the computation using empirically estimated inverse covariance weighting 
($\textbf{R} = \widehat{\textbf{C}}^{-1}$), the weighting scheme used in \citetalias{ali_et_al2015} which, with an empirically estimated covariance, leads to substantial loss. With this weighting, our 
expressions for $P_{\rm in}$ and $P_{\rm out}$ become:

@@

Phrased in the context of Bayes' rule, we wish to find the posterior probability distribution $p(P_{\rm in} | 
P_{\rm out})$, which is the probability of $P_{\rm in}$ given the uncorrected/measured power spectrum estimate $P_{\rm out}$. Bayes' rule gives

@@

Going forward, we treat every $k$-value separately in order to determine an upper limit on EoR per $k$. For every injection level, we smooth the distribution of $P_{\rm out}$ values using kernel density estimators (\citealt{scott2008kernel}), normalizing each one. Stitching all of them together results in a 2-dimensional smoothed transfer function, shown in Figure \ref{fig:sigloss_transfercurve} for empirical inverse covariance weighting (left) and uniform weighting (right). Although we only show figures for one $k$-value, we note that 
the shape of the transfer curve is nearly identical for all $k$'s. This transfer function is the likelihood function in Bayes' rule, namely $\mathcal{L} (  P_{\rm out} | P_{\rm in})$. After multiplying by the prior, we then simply take a horizontal cut across at the data value $P_{\rm out}$ to yield a posterior distribution for the signal. We compute the $95\%$ confidence interval (an upper limit on EoR) from these distributions.

@@

By-eye inspection of the transfer function plot in Figure \ref{fig:sigloss_transfercurve} gives a sense of what the signal loss result should be. The power spectrum value of our data, $
\widehat{\textbf{p}}_{x}$ is marked by the solid gray horizontal lines. From the left plot (empirical inverse covariance weighting), one can eyeball that a data value of $10^{4} \, mK^{2} (h^{-1} Mpc)^{3}$, for example, would map approximately to a 
value of $\sim10^{8} \, mK^{2} (h^{-1} Mpc)^{3}$, implying a signal loss factor of $\sim10000$. For the uniform-weighted case (right plot), we see no loss at a data value of $\sim10^{7} \, mK^{2} (h^{-1} Mpc)^{3}$.

@@

\begin{figure*}
	\centering
	\includegraphics[width=1\textwidth]{plots/sigloss_transfercurve_posneg.png}
	\caption{Signal loss transfer functions showing the relationship of $P_{\rm in}$ and $\widehat{\textbf{p}}_{r}$, as defined by Equations \eqref{eq:Pin} and \eqref{eq:sigloss}. Power spectra values (black points) are generated for $20$ realizations of $\textbf{e}$ per signal injection level. Kernel density estimations of the power spectrum transfer functions are shown as colored 
heat-maps on top of the points for the cases of empirical inverse covariance weighted PAPER-64 data (left) and uniform-weighted data (right). The dotted black 
diagonal lines mark a perfect unity mapping, and the solid gray horizontal line denotes the power spectrum value of the data $\widehat{\textbf{p}}_{x}$, from which a posterior distribution for the signal is extracted. From these plots, it is clear that the weighted case results in over $\sim3$ orders of magnitude of signal loss at the data level, whereas the uniform-weighted case does 
not exhibit loss. The general shape of these transfer functions are also shown by the black curves in Figure \ref{fig:sigloss_terms} for comparison.}
	\label{fig:sigloss_transfercurve}
\end{figure*}

@@

The loss-corrected power spectrum result for empirical inverse covariance weighted PAPER-64 data is shown in Figure \ref{fig:ps2_data} (black dashed), which we can compare to the original lossy result (black and gray points). %There are a few important checks to examine. First, we see that the uniform-weighted power spectrum $2\sigma$ upper limit (dashed blue) is identical in both panels. This is an important check, as we expect no signal loss for this case. Any difference here would indicate an error in the pipeline or discrepancy in the range of data included. Additionally, it is clear that the power spectrum, prior to signal loss estimation, is inconsistent with the (now revised) theoretical noise level prediction. 
Post-signal loss estimation, the power spectrum limits are higher than both the theory (green) and uniform-weighted power spectrum (blue dashed), a consequence of weighting with a steep eigenspectrum where the `weak' modes are strongly coupled to the time-averaged fringe-rate filtered data. We elaborate on this point in the next section, as well as investigate alternate 
weighting schemes to empirical inverse covariance weighting, with the goal of finding one that balances the aggressiveness of down-weighting contaminants and minimizing the loss of EoR signal.

\begin{figure*}
	\centering
	\includegraphics[width=0.4\textwidth]{plots/ps1_data.png}
	\includegraphics[width=0.4\textwidth]{plots/ps2_data.png}
	\caption{Empirical inverse covariance weighted power spectrum of PAPER-64 data pre-signal loss estimation (positive points in black and negative points in gray, 
with $2\sigma$ error bars). The dashed black curve is the $2\sigma$ upper limit on the EoR signal post-signal loss estimation. The dashed blue line is the uniform-weighted power 
spectrum ($2\sigma$ upper limit). The solid green line is the theoretical $2\sigma$ noise level prediction based on observational 
parameters, whose calculation is detailed in Section \ref{sec:PSSense}.}
	\label{fig:ps2_data}
\end{figure*}

@@

We also saw in Section \ref{sec:otherweight} how adding the identity matrix to the empirical covariance can minimize signal loss. We experiment with this idea as well, shown in the bottom panel of Figure \ref{fig:sigloss_modeloop}. The grey and black lines represent power spectrum limits pre and post signal loss estimation, respectively, as a function of the strength of $\textbf{I}$ that is added to $\widehat{\textbf{C}}$, quantified as the percentage of the $Tr(\widehat{\textbf{C}})$ added to $\widehat{\textbf{C}}$. When $0\%$  of the $Tr(\widehat{\textbf{C}})$ is used, it is equivalent to the empirical inverse covariance weighted case. From this plot we see that only a small percentage of $Tr(\widehat{\textbf{C}})$ is needed to significantly reduce loss. We expect that as the strength of $\textbf{I}$ is increased (going to the left), both the black and gray curves will approach the uniform-weighted case.

\begin{figure*}
	\centering
	\includegraphics[width=1\textwidth]{plots/sigloss_modeloop_2panel.png}
	\caption{Power spectra $2\sigma$ upper limits for $k=0.393$ h Mpc$^{-1}$ for fringe-rate filtered PAPER-64 data. Top: Values 
are shown before (gray) and after (black) signal loss estimation as a function of number of eigenmodes of $\widehat{\textbf{C}}$ that 
are down-weighted. This regularization knob is tuned from $0$ modes on the left (i.e. unweighted) to $21$ modes on the right (i.e. full inverse 
covariance weighting). Over $\sim3$ orders of magnitude of signal loss results when using empirical inverse covariance weighting. Bottom: Power spectrum upper limits before (gray) and after (black) signal loss estimation as a function of identity added to the empirical covariance. This regularization knob is tuned from $0\%$  of the $Tr(\widehat{\textbf{C}})$ added to $\widehat{\textbf{C}}$ on the right (i.e. empirical inverse covariance weighting) to $20\%$ of $Tr(\widehat{\textbf{C}})$ added to $\widehat{\textbf{C}}$ on the left. Also 
plotted in both panels for comparison are $2\sigma$ power spectrum upper limits for the uniform-weighted case (dashed blue) and inverse variance 
weighted case (red); both are after signal loss estimation. Finally, a theoretical prediction for noise ($2\sigma$ error) is plotted 
as solid green. In the revised PAPER-64 analysis in this paper, we choose to use a regularization scheme of $\widehat{\textbf{C}} \equiv 0.04Tr(\widehat{\textbf{C}}) + \widehat{\textbf{C}}$ because it slightly outperforms both the down-weighting individual eigenmodes and inverse variance cases.}
	\label{fig:sigloss_modeloop}
\end{figure*}

@@

\begin{figure}[tp]
\centering
\includegraphics[width=\textwidth]{plots/method2_heatmap_posneg.png}
\caption{The distribution of $\widehat{\textbf{p}}_{r}$ values for a 
given injection level P$_{\rm in}$. The $\widehat{\textbf{p}}_{r}$ values that are plotted on the y-axis represent the weighted power spectrum of data plus the injected signal. It differs from that of Figure \ref{fig:sigloss_transfercurve} by not subtracting off the power spectrum of data alone (not subtracting off the second term in Equation \eqref{eq:sigloss}). We show kernel density estimations of the power spectrum transfer functions as colored heat-maps for the cases of empirical inverse covariance weighted PAPER-64 data (left) and uniform-weighted data (right). The dotted black 
diagonal lines mark a perfect unity mapping, and the solid gray horizontal line denotes the peak of $\widehat{\textbf{p}}_{x}$, the data distribution. At low injection, $\widehat{\textbf{p}}_{r}$ converges to the data level.
}
\label{fig:Pr_vs_Pin}
\end{figure}
